Blocking-resistant communication\\through domain fronting

### 2015-01-12 docs/meek.tex
Shorter sessions IDs in diagram.
https://trac.torproject.org/projects/tor/ticket/12778

\begin{figure}
\scriptsize
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
Content-Length: 517

@@

\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75...
\end{verbatim}
\end{quote}
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
Content-Length: 0

>>>>

\begin{figure}
\scriptsize
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1HnR
Content-Length: 517

@@

\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75...
\end{verbatim}
\end{quote}
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1HnR
Content-Length: 0
